# Vietnam

Field work in Vietnam consisted of a qualitative assessment with focus group discussions and quantitative surveys. We first look at the consolidated survey results.

Notes:   

- 1 Int'l \$ = 7,473.67 VND (Vietnamese Dong) using [2020 World Bank PPP conversion rates](https://data.worldbank.org/indicator/PA.NUS.PPP) (1 Int'l \$ = 1 USD)
- Focus crop = **rice**
- Transportation costs are lumped into the cost of pesticides, fertilizers and harvesting.
- Labor costs are per hectare
- Inspection and certification fees are per farm (total fees for a single season). Only farmers who sell to **seed centers** or **seed companies** do incur these marketing costs.

## Survey Codebook

```{r}

xrate <- 7473.67

# Load respondent data
hh <- fread("../data/vnm/hh.csv")
# Load group data
group <- fread("../data/vnm/group.csv")
# Load final codebook
lbl <- fread("../data/codebook.csv")

```

There are `r ncol(hh)` variables and `r nrow(hh)` observations in this set. A detailed codebook is shown below.

```{r}

kbl(lbl[label %in% names(hh)], align="llccc", caption="Survey Codebook")

```

Recode variable names.

```{r}

setnames(hh, lbl$label, lbl$code, skip_absent=T)

```

Additional recodes for categorical variables. Note that we create a categorical variable `ssd` to indicate whether a farmer currently engages in formal seed system distribution.

```{r}

setorder(hh, adm1_nm, group, gender)

hh[, `:=`(
  hhid = paste("VNM", gsub(" ", "0", format(1:.N, width=3)), sep=""),
  iso3 = "VNM",
  crop = "rice",
  adm1_nm = factor(adm1_nm),
  group = factor(group, levels=hh[, unique(group)]),
  gender = factor(gender, labels=c(Nam="Male", Nữ="Female")),
  ssd = factor(cert_lcu > 0, labels=c("Informal", "Formal"))
)]

```


## Data Enrichment

Below we append some of the information that was recorded at the group level.

```{r}

kbl(group, align="lccccccc")

# Merge
hh[group, on=.(group=Group), `:=`(
  group_year = `Established`,
  group_size = `Members`,
  soil_type = `Soil`,
  seasons = `Seasons`,
  irrigated = `Irrigation`,
  market_access = `Market access`,
  ttrade = `Transboundary trade`
)]

```


### Spatial Covariates

Using **community GPS coordinates** we also suggest to enrich this dataset with additional biophysical and geospatial variables, e.g.:

- Agroecological zone
- Travel time to nearest market
- Distance to nearest seed center / company
- Size of nearest seed center / company
- Population density
- Last season total rainfall
- Last season heat stress days (if any)

[pending GPS coordinates]


### Constructed Variables

We check farmer-reported total costs `costs_ha_lcu` against the sum of individual cost line items.

```{r}

hh[, 
  tran_ha_lcu := as.numeric(tran_ha_lcu)
][, 
  tran_ha_lcu := fifelse(is.na(tran_ha_lcu), 0, tran_ha_lcu)
][, costs_ha_lcu_imp := 
    # Per ha costs
    seed_ha_lcu + fert_ha_lcu + pest_ha_lcu + tran_ha_lcu + labor_ha_lcu + cert_lcu +
    # Per kg costs
    yield_ha_kg * (labl_kg_lcu + pckg_kg_lcu + mark_kg_lcu)]

hh[, summary(costs_ha_lcu_imp - costs_ha_lcu)]

```

There is no discrepancy between the 2 quantities, so we can assume that total costs are constructed per the formula above. No error was found.

We also check that farmer-reported sales and profit margins are consistent.

```{r}

hh[, summary(sales_ha_lcu - (sales_kg_lcu * sales_ha_kg))]

```

Further we construct gross margin per ha `margin_ha_lcu`, total sales `sales_ha_sh` and profit margin `margin_ha_sh` per unit of (variable) input costs, and `costs_ha_ppp`, `sales_ha_ppp` and `margin_ha_ppp` in PPP terms to allow for comparisons across groups and countries. 

We also construct a measure of **total factor productivity** `tfp` as output per unit of input costs. Strictly speaking it is only "partial factor productivity" here because we don't include the rental cost of land, land preparation costs, irrigation costs, and the costs of animal and mechanical implements.

```{r}

hh[, `:=`(
  margin_ha_lcu = sales_ha_lcu - costs_ha_lcu
)][, `:=`(
  sales_ha_sh = sales_ha_lcu / costs_ha_lcu,
  margin_ha_sh = margin_ha_lcu / costs_ha_lcu,
  costs_ha_ppp = costs_ha_lcu / xrate,
  sales_ha_ppp = sales_ha_lcu / xrate,
  margin_ha_ppp = margin_ha_lcu / xrate
)][, `:=`(
  tfp = yield_ha_kg / costs_ha_ppp
)]

```

Finally we normalize all farmer cost line items into a "long" table `hh_prod_cost` for charting.

```{r}

# Normalize production cost table
hh_prod_cost <- hh[, .(hhid,
  Seeds = seed_ha_lcu, 
  Fertilizer = fert_ha_lcu, 
  Pesticides = pest_ha_lcu, 
  Transport = tran_ha_lcu, 
  Labor = labor_ha_lcu, 
  Certification = cert_lcu,
  Labeling = yield_ha_kg * labl_kg_lcu,
  Packaging = yield_ha_kg * pckg_kg_lcu,
  Marketing = yield_ha_kg * mark_kg_lcu
)]

hh_prod_cost <- melt(hh_prod_cost, id.vars=1, value.name="lcu", variable.name="type")
hh_prod_cost[hh, on=.(hhid), `:=`(
  # Add types
  group = i.group,
  gender = i.gender,
  crop = i.crop,
  ssd = i.ssd
)][, `:=`(
  # Add cost shares and PPP terms
  share = lcu/sum(lcu, na.rm=T),
  ppp = lcu/xrate
), by=.(hhid)]

```

Note that in the current survey we are missing **farm sizes** (or planted acreage), so we can not directly study the effect of farm size on the per-unit costs of production and yields, or look at potential **scale effects** on a farmer's **efficiency** and **profitability**. We can however study whether larger groups might have positive effects.


## Descriptive Statistics

### Respondent Characteristics

First a breakdown by group.

```{r, fig.height=3.5}

ggplot(
  hh[, .N, by=.(adm1_nm, group, ssd, gender)],
  aes(axis1=adm1_nm, axis2=gender, axis3=ssd, y=N)) +
  geom_alluvium(aes(fill=group), width=1/4) +
  geom_stratum(width=1/4) +
  geom_text(stat="stratum", aes(label=after_stat(stratum)), angle=90, size=2.2) +
  scale_x_discrete(limits=c("Province", "Gender", "Seed Distribution")) +
  labs(y=NULL, fill="Seed Club",
    title = "Survey Respondents (Vietnam)",
    subtitle = "Stratified by club and demographics (N = 60)") +
  theme_def(axis.text=element_text(face="bold"))


```

Showing contingency table between each pair of categorical variables (seed club `group`, `gender`, and use of formal seed system distribution `ssd`). Rice in Vietnam is a male-dominated production, hence the absence of female respondents in a few clubs.

```{r}

ttt_ftable(hh, vars=c("group", "gender", "ssd"))

```

Mantel-Haenszel test shows weak association between the 3 variables. This is further shown in the 2x2 mosaic plots below (standardized residuals between [-2,2]).

```{r, out.width="50%", fig.show="hold", fig.asp=1}

mosaicplot(~gender+ssd, hh, shade=T,
  main=NA, xlab="Gender", ylab="Seed System")

mosaicplot(~adm1_nm+ssd, hh, shade=T,
  main=NA, xlab="Province", ylab="Seed System")

```

NB. blue means there are more observations in the cell than would be expected under the null model (independence). Red means there are fewer observations than would have been expected.



### Seed Production Costs

We then look at the general breakdown and distribution of input costs across seed clubs, gender, and input type.

```{r, out.width="50%", fig.show="hold", fig.width=2.5, fig.asp=1}

ggplot(hh, aes(gender, costs_ha_ppp, fill=gender)) +
  geom_boxplot(alpha=.7) +
  scale_y_continuous(labels=comma) +
  facet_wrap(~crop) +
  labs(x="", y="", fill="",
    title="Total Input Costs (PPP$ / ha) - Vietnam",
    subtitle="Stratified by gender") +
  theme_def(legend.position="none")

ggplot(hh, aes(group, costs_ha_ppp, fill=group)) +
  geom_boxplot(alpha=.7) +
  scale_y_continuous(labels=comma) +  
  facet_wrap(~crop) +
  labs(x="", y="", fill="",
    title="Total Input Costs (PPP$ / ha) - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="none")

```

Breakdown across categories of farm input.

```{r}

tbl <- hh_prod_cost[, .(
  share = mean(share, na.rm=T)
), keyby=.(gender, ssd, type)]

ggplot(tbl, aes(gender, share, fill=type)) +
  geom_bar(stat="identity", alpha=.8, width=.6) +
  scale_y_continuous(labels=percent) +
  scale_fill_manual("", values=colorRampPalette(pal)(9)) +
  facet_wrap(~ssd) +
  labs(y="", x="",
    title="Breakdown of Input Costs by Category - Vietnam",
    subtitle="Stratified by gender and seed system") +
  theme_def()

```

```{r}

tbl <- hh_prod_cost[, .(
  share = mean(share, na.rm=T)
), keyby=.(group, ssd, type)]

ggplot(tbl, aes(group, share, fill=type)) +
  geom_bar(stat="identity", alpha=.8, width=.6) +
  scale_y_continuous(labels=percent) +
  scale_fill_manual("", values=colorRampPalette(pal)(9)) +
  facet_wrap(~ssd, scales="free_x") +
  labs(y="", x="",
    title="Breakdown of Input Costs by Category - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def()

```

Are there significant differences across groups?

```{r}

ggplot(hh_prod_cost[!type %in% c("Transport", "Marketing")], 
  aes(type, ppp, fill=gender)) +
  geom_boxplot(alpha=.7) +
  scale_y_continuous(labels=comma) +
  coord_flip() +
  facet_wrap(~crop) +  
  labs(x="", y="", fill="",
    title="Input Costs by Category (PPP$ by Hectare) - Vietnam",
    subtitle="Stratified by gender") +
  theme_def(legend.position="top")

ggplot(hh_prod_cost[!type %in% c("Transport", "Marketing")], 
  aes(type, ppp, fill=group)) +
  geom_boxplot(alpha=.7) +
  scale_y_continuous(labels=comma) +  
  coord_flip() +
  facet_wrap(~crop) +  
  labs(x="", y="", fill="",
    title="Input Costs by Category (PPP$ by Hectare) - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="top")

```


### Efficiency

Differences in productivity measures across groups?

```{r}

fmt <- function(x) c(Mean=comma(mean(x, na.rm=T)), SD=comma(sd(x, na.rm=T)))
ttt(yield_ha_kg ~ group | gender, data=hh, render=fmt,
  caption="Rice Seed Yield (kg / ha) - Vietnam")

```

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggplot(hh, aes(gender, yield_ha_kg, fill=gender)) +
  geom_boxplot(alpha=.7) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Rice Seed Yield (kg / ha) - Vietnam",
    subtitle="Stratified by gender") +
  theme_def(legend.position="none")

ggplot(hh, aes(gender, sales_ha_ppp, fill=gender)) +
  geom_boxplot(alpha=.7) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Total Seed Sales (PPP$ / ha) - Vietnam",
    subtitle="Stratified by gender") +
  theme_def(legend.position="none")

```


```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggplot(hh, aes(group, yield_ha_kg, fill=group)) +
  geom_boxplot(alpha=.7) +
  scale_x_discrete(labels=label_wrap(5)) +
  scale_y_continuous(labels=comma) +  
  labs(x="", y="", fill="",
    title="Rice Seed Yield (Kg / ha) - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="none")

ggplot(hh, aes(group, sales_ha_ppp, fill=group)) +
  geom_boxplot(alpha=.7) +
  scale_x_discrete(labels=label_wrap(5)) +
  scale_y_continuous(labels=comma) +  
  labs(x="", y="", fill="",
    title="Total Seed Sales (PPP$ / ha) - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="none")

```

Looking at **production frontiers** (units of output vs. units of input). We expect S-shape curves with farmers at different levels of technical efficiency along the curve. 

NB. Farmer `VNM013` in Winh Qui has total costs over PPP$ 4,000/ha. He was excluded from the approximation (in red below).

```{r}

outlier <- "VNM013"

ggplot(hh[!hhid %in% outlier], aes(costs_ha_ppp, yield_ha_kg)) +
  geom_smooth(size=.8) +
  geom_point(alpha=.7, shape=20, color=1) +
  geom_point(data=hh[hhid %in% outlier], aes(costs_ha_ppp, yield_ha_kg), 
    alpha=.7, color=2, shape=18) +
  scale_x_continuous(labels=comma) +
  scale_y_continuous(labels=comma) +
  coord_cartesian(ylim=c(4000, 14000)) +
  labs(x="", y="",
    title="Production Frontier (Output vs. Input) - Vietnam",
    subtitle="Each point is a respondent (kg vs. PPP$ / ha)") +
  theme_def(legend.position="none")

```

```{r}

ggplot(hh[!hhid %in% outlier], aes(costs_ha_ppp, yield_ha_kg)) +
  geom_smooth(aes(color=gender, fill=gender), size=.8, level=.9) +
  geom_point(alpha=.7, shape=20) +
  scale_x_continuous(labels=comma) +
  scale_y_continuous(labels=comma) +
  facet_wrap(~gender, scales="free_x") +
  coord_cartesian(ylim=c(4000, 14000)) +
  labs(x="", y="",
    title="Production Frontier (Output vs. Input) - Vietnam",
    subtitle="Each point is a respondent. Shade shows 90% CI (kg vs. PPP$ / ha)") +
  theme_def(legend.position="none")

```

```{r}

ggplot(hh[!hhid %in% outlier], aes(costs_ha_ppp, yield_ha_kg)) +
  geom_smooth(aes(color=group, fill=group), size=.8, level=.9) +
  geom_point(alpha=.7, shape=20) +
  scale_x_continuous(labels=comma) +
  scale_y_continuous(labels=comma) +
  facet_wrap(~group) +
  coord_cartesian(ylim=c(4000, 14000)) +
  labs(x="", y="",
    title="Production Frontier (Output vs. Input) - Vietnam",
    subtitle="Each point is a respondent. Shade shows 90% CI (kg vs. PPP$ / ha)") +
  theme_def(legend.position="none")


```



### Profitability

```{r}

fmt <- function(x) c(Mean=comma(mean(x, na.rm=T)), SD=comma(sd(x, na.rm=T)))
ttt(margin_ha_ppp ~ group | gender, data=hh, render=fmt,
  caption="Mean Gross Profit Margin in Absolute Terms (PPP$ / ha) - Vietnam")

fmt <- function(x) c(Mean=percent(mean(x, na.rm=T)), SD=percent(sd(x, na.rm=T)))
ttt(margin_ha_sh ~ group | gender, data=hh, render=fmt,
  caption="Mean Gross Profit Margin in Relative Terms (% of variable input costs) - Vietnam")

```

```{r}

ggplot(hh, aes(x=1:nrow(hh), color=group)) +
  geom_linerange(aes(ymin=costs_ha_ppp, ymax=sales_ha_ppp, linetype=gender), size=.6) +
  geom_point(aes(y=costs_ha_ppp), shape=20, size=1.4) +
  geom_point(aes(y=sales_ha_ppp), shape=17, size=1.4) +
  scale_y_continuous(labels=comma) +
  labs(x=NULL, y=NULL, color="", linetype="",
    title="Profit Margin (PPP$ / ha) - Vietnam",
    subtitle="Each bar is a respondent's gross profit margin") +
  theme_def(legend.position="right")

```

Farmers' gross profit margins by gender and across groups in both absolute terms and in relative terms as percentage of total costs per hectare.

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggplot(hh, aes(gender, margin_ha_ppp, fill=gender)) +
  geom_boxplot(alpha=.7) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Absolute Terms - Vietnam",
    subtitle="Stratified by gender (PPP$ / ha)") +
  theme_def(legend.position="none")

ggplot(hh, aes(gender, margin_ha_sh, fill=gender)) +
  geom_boxplot(alpha=.7) +
  scale_y_continuous(labels=percent) +
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Relative Terms - Vietnam",
    subtitle="Stratified by gender (% of total costs)") +
  theme_def(legend.position="none")

```

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggplot(hh, aes(group, margin_ha_ppp, fill=group)) +
  geom_boxplot(alpha=.7) +
  scale_x_discrete(labels=label_wrap(5)) +
  scale_y_continuous(labels=comma) +  
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Absolute Terms - Vietnam",
    subtitle="Stratified by seed club (PPP$ / ha)") +
  theme_def(legend.position="none")

ggplot(hh, aes(group, margin_ha_sh, fill=group)) +
  geom_boxplot(alpha=.7) +
  scale_x_discrete(labels=label_wrap(5)) +  
  scale_y_continuous(labels=percent) +  
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Relative Terms - Vietnam",
    subtitle="Stratified by seed club (% of total costs)") +
  theme_def(legend.position="none")

```

## Correlation

Significant associations. 

```{r, fig.height=5}

ggpairs(
  hh[, .(`seed club`=group, age, `costs`=costs_ha_ppp, `seed yield`=yield_ha_kg,
    `margin PPP$`=margin_ha_ppp, `margin %`=margin_ha_sh)],
  upper = list(
    continuous="cor", 
    combo=wrap("summarise_by", color=pal, size=2)),
  lower = list(
    continuous=wrap("smooth", shape=NA), 
    combo=wrap("box_no_facet", fill=pal, alpha=.8)),
  diag = list(
    continuous=wrap("densityDiag", fill=NA),
    discrete=wrap("barDiag", fill=pal, alpha=.8)),
  title="Correlogram stratified by seed club - Vietnam"
) + theme_def(
  strip.text=element_text(hjust=.5),
  panel.grid.major=element_blank()
)

```

```{r, fig.height=5}

ggpairs(
  hh[, .(gender, age, `costs`=costs_ha_ppp, `seed yield`=yield_ha_kg, 
    `margin PPP$`=margin_ha_ppp, `margin %`=margin_ha_sh)],
  upper = list(
    continuous="cor", 
    combo=wrap("summarise_by", color=pal[1:2], size=2)),
  lower = list(
    continuous=wrap("smooth", shape=NA, color=hh[, pal[gender]]), 
    combo=wrap("box_no_facet", fill=pal[1:2], alpha=.8)),
  diag = list(
    continuous=wrap("densityDiag", fill=NA),
    discrete=wrap("barDiag", fill=pal[1:2], alpha=.8)),
  title="Correlogram stratified by gender - Vietnam"
) + theme_def(
  strip.text=element_text(hjust=.5),
  panel.grid.major=element_blank()
)

```

## Clustering

[TBD]



```{r save-vnm}

rm(tmp, x, y, i, fmt)
saveRDS(hh, "../tmp/data_vnm.rds")

```

