# Vietnam

Field work in Vietnam consists of a qualitative assessment with focus group discussions and quantitative surveys. We first look at the consolidated survey results.

Notes:   

- 1 Int'l \$ = 7,473.67 VND (Vietnamese Dong) using [2020 World Bank PPP conversion rates](https://data.worldbank.org/indicator/PA.NUS.PPP) (1 Int'l \$ = 1 USD)
- Focus crop = **rice**
- Transportation costs are lumped into the cost of pesticides, fertilizers and harvesting.
- Labor costs are per hectare
- Inspection and certification fees are per farm (total fees for a single season). Only farmers who sell to **seed centers** or **seed companies** do incur these marketing costs.
- We differentiate between expected yield per ha `yield_ha_kg` and realized sales in the last season `sales_ha_kg`.

## Survey Recodes

```{r vnm}

xrate <- 7473.67

# Load respondent data
hh <- fread("../data/vnm/hh.csv")
# Load group data
group <- fread("../data/vnm/group.csv")

```

There are `r ncol(hh)` variables and `r nrow(hh)` observations in this set. A summary is shown below.

```{r}

print(dfSummary(hh), max.tbl.height=500)

```

Recode variable names (see [codebook](index.html#objectives)).

```{r}

setnames(hh, lbl$label, lbl$code, skip_absent=T)

```

Additional recodes for categorical variables. Note that we create a categorical variable `ssd` to indicate whether a farmer currently engages in formal seed system distribution. For consistency across countries we also reclassify `age` into 2 categories `< 30` and `≥ 30`.

```{r}

setorder(hh, adm1_nm, group, gender)

hh[, `:=`(
  hhid = paste("VNM", gsub(" ", "0", format(1:.N, width=3)), sep=""),
  iso3 = "VNM",
  crop = "rice",
  adm1_nm = factor(adm1_nm),
  group = factor(group, levels=hh[, unique(group)]),
  gender = factor(gender, levels=c("Nam", "Nữ"), labels=c("Male", "Female")),
  ssd = factor(cert_lcu > 0, levels=c(F, T), labels=c("Informal", "Formal")),
  age_num = age,
  age = factor(age >= 30, levels=c(F, T), labels=c("< 30", "≥ 30")),
  years = factor(member_years >= 5, levels=c(F, T), labels=c("< 5", "≥ 5"))
)]

```

### Spatial Covariates

Using **community GPS coordinates** we also suggest to enrich this dataset with additional biophysical and geospatial variables, e.g.:

- Agroecological zone
- Travel time to nearest market
- Distance to nearest seed center / company
- Size of nearest seed center / company
- Population density
- Last season total rainfall
- Last season heat stress days (if any)

[pending GPS coordinates]


### Constructed Variables

Farmers report both expected yields `yield_ha_kg` and actual sales in the last season `sales_ha_kg`, so we can construct both **expected** and **realized** costs in monetary terms `costs_exp_ha_lcu` and `costs_real_ha_lcu`. Note that we then use **realized** sales to calculate profitability metrics.

```{r}

hh[, 
  tran_ha_lcu := as.numeric(tran_ha_lcu)
][, 
  tran_ha_lcu := fifelse(is.na(tran_ha_lcu), 0, tran_ha_lcu)
][, `:=`(
  # Expected costs
  costs_exp_ha_lcu = 
    # Per ha costs
    seed_ha_lcu + fert_ha_lcu + pest_ha_lcu + tran_ha_lcu + labor_ha_lcu + cert_lcu +
    # Per kg costs
    yield_ha_kg * (labl_kg_lcu + pckg_kg_lcu + mark_kg_lcu),  
  
  # Realized costs
  costs_real_ha_lcu = 
    # Per ha costs
    seed_ha_lcu + fert_ha_lcu + pest_ha_lcu + tran_ha_lcu + labor_ha_lcu + cert_lcu +
    # Per kg costs
    sales_ha_kg * (labl_kg_lcu + pckg_kg_lcu + mark_kg_lcu)
)]

```

Using **realized** costs and sales, we construct gross margin per ha `margin_ha_lcu`, total sales `sales_ha_sh` and profit margin `margin_ha_sh` per unit of (variable) input costs, and `costs_ha_ppp`, `sales_ha_ppp` and `margin_ha_ppp` in PPP terms to allow for comparisons across groups and countries. 

We also construct a measure of **total factor productivity** `tfp` as **expected** output per unit of (expected) input costs. Strictly speaking it is only "partial factor productivity" here because we don't include the rental cost of land, land preparation costs, irrigation costs, and the costs of animal and mechanical implements.

```{r}

hh[, `:=`(
  sales_exp_ha_lcu = yield_ha_kg * sales_kg_lcu,
  sales_real_ha_lcu = sales_ha_kg * sales_kg_lcu
)][, `:=`(
  margin_ha_lcu = sales_real_ha_lcu - costs_real_ha_lcu
)][, `:=`(
  # Shares
  sales_ha_sh = sales_real_ha_lcu / costs_real_ha_lcu,
  margin_ha_sh = margin_ha_lcu / costs_real_ha_lcu,
  # PPP$
  costs_ha_ppp = costs_real_ha_lcu / xrate,
  sales_ha_ppp = sales_real_ha_lcu / xrate,
  margin_ha_ppp = margin_ha_lcu / xrate
)][, `:=`(
  tfp = yield_ha_kg / (costs_exp_ha_lcu / xrate)
)]

```

Below we append some of the information that was recorded at the group level.

```{r}

kbl(group, align="lccccccc")

# Merge
hh[group, on=.(group=Group), `:=`(
  group_year = `Established`,
  group_size = `Members`,
  soil_type = `Soil`,
  seasons = `Seasons`,
  irrigated = `Irrigation`,
  market_access = `Market access`,
  ttrade = `Transboundary trade`
)]

```

Finally we normalize all farmer cost line items into a "long" table `hh_prod_cost` for charting.

```{r}

# Normalize production cost table
hh_prod_cost <- hh[, .(hhid,
  Seeds = seed_ha_lcu, 
  Fertilizer = fert_ha_lcu, 
  Pesticides = pest_ha_lcu, 
  Labor = labor_ha_lcu,
  Transport = tran_ha_lcu, 
  Certification = cert_lcu,
  Labeling = sales_ha_kg * labl_kg_lcu,
  Packaging = sales_ha_kg * pckg_kg_lcu,
  Marketing = sales_ha_kg * mark_kg_lcu
)]

hh_prod_cost <- melt(hh_prod_cost, id.vars=1, value.name="lcu", variable.name="type")


```

And we lump all marketing costs into a single category.

```{r}

levels(hh_prod_cost$type) <- levels(hh_prod_cost$type)[c(1,2,3,4,9,9,9,9,9)]

hh_prod_cost <- hh_prod_cost[, .(
  lcu = sum(lcu, na.rm=T)
), by=.(hhid, type)
][, `:=`(
  # Add cost shares and PPP terms
  share = lcu/sum(lcu, na.rm=T),
  ppp = lcu/xrate
), by=.(hhid)
][hh, on=.(hhid), `:=`(
  # Add categorical variables
  group = group,
  gender = gender,
  age = age,
  years = years,
  crop = crop,
  ssd = ssd
)]

```

Note that in the current survey we are missing **farm sizes** (or planted acreage), so we can not directly study the effect of farm size on the per-unit costs of production and yields, or look at potential **scale effects** on a farmer's **efficiency** and **profitability**. We can however study whether larger groups might have positive effects.


## Descriptive Statistics

### Respondent Characteristics

Breakdown by categorical variables.

```{r, fig.height=3.5}

ggplot(
  hh[, .N, by=.(group, age, gender, crop, years)],
  aes(axis1=crop, axis2=gender, axis3=age, axis4=years, y=N)) +
  geom_alluvium(aes(fill=group), width=1/4, alpha=.7, color="white") +
  geom_stratum(width=1/4) +
  geom_text(stat="stratum", aes(label=after_stat(stratum)), angle=90, size=2.2) +
  scale_x_discrete(limits=c("Crop", "Gender", "Age", "Years in Seed Club")) +
  labs(y=NULL, fill="Seed Club",
    title = "Categories of Survey Respondents - Vietnam",
    subtitle = "Stratified by seed club") +
  theme_def(axis.text=element_text(face="bold"))

```

Showing contingency tables between each pair of categorical variables (seed club `group`, `gender`, years in seed club `years`, and use of formal seed system distribution `ssd`). Rice in Vietnam is a male-dominated production, hence the absence of female respondents in a few clubs.

```{r}

ttt_ftable(hh, vars=c("group", "gender", "years"))

```


### Seed Production Costs

General breakdown and distribution of (realized) input costs across seed clubs, gender, and input type.

```{r}

ttt(costs_ha_ppp ~ group | gender, data=hh, render=fmt,
  caption="Total Input Costs in Absolute Terms (PPP$ / ha) - Vietnam")

```

Boxplots with mean comparison p-value and significance levels. Each level is **compared to the sample mean**.

(ns : p > 0.05, * : p ≤ 0.05, ** : p ≤ 0.01, *** = p ≤ 0.001, **** = p ≤ 0.0001)

```{r, out.width="50%", fig.show="hold", fig.width=2.5, fig.asp=1}

ggBoxTest(hh, aes(gender, costs_ha_ppp, fill=gender, color=gender), cp=list(1:2)) +
  scale_y_continuous(labels=comma) +
  facet_wrap(~crop) +
  labs(x="", y="", fill="",
    title="Total Input Costs (PPP$ / ha) - Vietnam",
    subtitle="Stratified by gender") +
  theme_def(legend.position="none")


ggBoxTest(hh, aes(group, costs_ha_ppp, fill=group, color=group), ref=".all.") +
  facet_wrap(~crop) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Total Input Costs (PPP$ / ha) - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="none")

```

Breakdown across categories of farm input.

```{r}

ttt(ppp ~ type | gender, data=hh_prod_cost, render=fmt,
  caption="Input Costs in Absolute Terms by Gender (PPP$ / ha) - Vietnam")

```

```{r}

tbl <- hh_prod_cost[, .(
  ppp = mean(ppp, na.rm=T)
), keyby=.(gender, ssd, type)]

ggplot(tbl, aes(gender, ppp, fill=type)) +
  geom_bar(stat="identity", position="fill", alpha=.7, width=.6, color="white") +
  scale_y_continuous(labels=percent) +
  facet_wrap(~ssd) +
  labs(y="", x="",
    title="Breakdown of Input Costs by Category - Vietnam",
    subtitle="Stratified by gender and seed system") +
  theme_def(legend.position="right")

```

```{r}

ttt(ppp ~ type | years, data=hh_prod_cost, render=fmt,
  caption="Input Costs in Absolute Terms by Years in Seed Group (PPP$ / ha) - Vietnam")

```

```{r}

tbl <- hh_prod_cost[, .(
  ppp = mean(ppp, na.rm=T)
), keyby=.(years, crop, type)]

ggplot(tbl, aes(years, ppp, fill=type)) +
  geom_bar(stat="identity", position="fill", alpha=.7, width=.6, color="white") +
  scale_y_continuous(labels=percent) +
  facet_wrap(~crop) +
  labs(y="", x="",
    title="Breakdown of Input Costs by Category - Vietnam",
    subtitle="Stratified by crop and years in seed club") +
  theme_def(legend.position="right")

```

```{r}

ttt(ppp ~ type | ssd, data=hh_prod_cost, render=fmt,
  caption="Input Costs in Absolute Terms by Seed System Type (PPP$ / ha) - Vietnam")

```

```{r}

tbl <- hh_prod_cost[, .(
  ppp = mean(ppp, na.rm=T)
), keyby=.(crop, group, type)]

ggplot(tbl, aes(group, ppp, fill=type)) +
  geom_bar(stat="identity", position="fill", alpha=.7, width=.6, color="white") +
  scale_y_continuous(labels=percent) +
  facet_wrap(~crop) +  
  labs(y="", x="",
    title="Breakdown of Input Costs by Category - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="right")

```

Are there significant differences across groups? We first compare input cost shares across gender, then across seed clubs.

```{r}

ggBoxTest(hh_prod_cost, 
  aes(type, share, fill=gender, color=gender), 
  grp.c=aes(group=type), grp.s=aes(group=gender)) +
  scale_y_continuous(labels=percent) +    
  facet_wrap(~crop) +  
  labs(x="", y="", fill="", color="",
    title="Input Costs by Category (Percent of Total Costs by Ha) - Vietnam",
    subtitle="Stratified by gender") +
  theme_def(legend.position="top")  

```

```{r}

ggBoxTest(hh_prod_cost, 
  aes(type, share, fill=group, color=group),
  grp.c=aes(group=type), grp.s=aes(group=group)) +
  scale_y_continuous(labels=percent) +  
  facet_wrap(~crop) +  
  labs(x="", y="", fill="", color="",
    title="Input Costs by Category (PPP$ by Hectare) - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="top")

```


### Efficiency

Differences in productivity measures (expected seed yields and sales) across groups.

```{r}

ttt(yield_ha_kg ~ group | gender+crop, data=hh, render=fmt,
  caption="Expected Rice Seed Yield (kg / ha) - Vietnam")
ttt(sales_ha_kg ~ group | gender+crop, data=hh, render=fmt,
  caption="Seed Sales (kg / ha) - Vietnam")

ttt(yield_ha_kg ~ group | years+crop, data=hh, render=fmt,
  caption="Realized Seed Sales (kg / ha) - Vietnam")
ttt(sales_ha_kg ~ group | years+crop, data=hh, render=fmt,
  caption="Realized Seed Sales (kg / ha) - Vietnam")

```

Differences in efficiency measures across gender with mean comparison (Wilcoxon) p-value.

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh, aes(gender, yield_ha_kg, color=gender, fill=gender), cp=list(1:2)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Expected Rice Seed Yield (kg / ha) - Vietnam",
    subtitle="Stratified by gender") +
  theme_def(legend.position="none")

ggBoxTest(hh, aes(gender, sales_ha_ppp, fill=gender), cp=list(1:2)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Total Seed Sales (PPP$ / ha) - Vietnam",
    subtitle="Stratified by gender") +
  theme_def(legend.position="none")

```

Differences in efficiency measures by years in seed club with mean comparison (Wilcoxon) p-value.

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh, aes(years, yield_ha_kg, color=years, fill=years), cp=list(1:2)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Expected Seed Yield (kg / ha) - Vietnam",
    subtitle="Stratified by years in seed club") +
  theme_def(legend.position="none")

ggBoxTest(hh, aes(years, sales_ha_ppp, color=years, fill=years), cp=list(1:2)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Total Seed Sales (PPP$ / ha) - Vietnam",
    subtitle="Stratified by years in seed club") +
  theme_def(legend.position="none")

```

Differences in efficiency measures across seed clubs with global ANOVA p-value.

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh, aes(group, yield_ha_kg, color=group, fill=group)) +
  scale_x_discrete(labels=label_wrap(5)) +
  scale_y_continuous(labels=comma) +  
  labs(x="", y="", fill="",
    title="Rice Seed Yield (Kg / ha) - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="none")

ggBoxTest(hh, aes(group, sales_ha_ppp, color=group, fill=group)) +
  scale_x_discrete(labels=label_wrap(5)) +
  scale_y_continuous(labels=comma) +  
  labs(x="", y="", fill="",
    title="Total Seed Sales (PPP$ / ha) - Vietnam",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="none")

```

Looking at **production frontiers** (units of output vs. units of input). We expect S-shape curves with farmers at different levels of technical efficiency along the curve. 

Note that Farmer `VNM013` in Winh Qui has total costs over PPP$ 4,000/ha. He was excluded from the approximated curves below.

```{r}

outlier <- hh[costs_ha_ppp > mean(costs_ha_ppp) + 3*sd(costs_ha_ppp), hhid]

kbl(
  caption="Farmers with total input costs > mean + 3*sd",
  hh[hhid %in% outlier, .(hhid, group, crop, yield_ha_kg, costs_ha_ppp)],
  format.args=list(big.mark=",", digits=0))

ggplot(hh[!hhid %in% outlier], aes(costs_ha_ppp, yield_ha_kg)) +
  geom_smooth(size=.8) +
  geom_point(alpha=.7, shape=20, color=1) +
  scale_x_continuous(labels=comma) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="",
    title="Production Frontier (Output vs. Input) - Vietnam",
    subtitle="Each point is a respondent. Shade shows 90% (kg vs. PPP$ / ha)") +
  theme_def(legend.position="none")

```

```{r}

ggplot(hh[!hhid %in% outlier], aes(costs_ha_ppp, yield_ha_kg)) +
  geom_smooth(aes(color=gender, fill=gender), size=.8, level=.9) +
  geom_point(alpha=.7, shape=20) +
  scale_x_continuous(labels=comma) +
  scale_y_continuous(labels=comma) +
  facet_wrap(~gender, scales="free_x") +
  labs(x="", y="",
    title="Production Frontier (Output vs. Input) - Vietnam",
    subtitle="Each point is a respondent. Shade shows 90% CI (kg vs. PPP$ / ha)") +
  theme_def(legend.position="none")

```

```{r}

ggplot(hh[!hhid %in% outlier], aes(costs_ha_ppp, yield_ha_kg)) +
  geom_smooth(aes(color=group, fill=group), size=.8, level=.9) +
  geom_point(alpha=.7, shape=20) +
  scale_x_continuous(labels=comma) +
  scale_y_continuous(labels=comma) +
  facet_wrap(~group) +
  coord_cartesian(ylim=c(4000, 14000)) +
  labs(x="", y="",
    title="Production Frontier (Output vs. Input) - Vietnam",
    subtitle="Each point is a respondent. Shade shows 90% CI (kg vs. PPP$ / ha)") +
  theme_def(legend.position="none")


```



### Profitability

Farmers' gross profit margins by gender and years in seed club.

```{r}

ttt(margin_ha_ppp ~ group | gender+years, data=hh, render=fmt,
  caption="Mean Gross Profit Margin in Absolute Terms (PPP$ / ha) - Vietnam")

ttt(margin_ha_sh ~ group | gender+years, data=hh, render=fmt_pct,
  caption="Mean Gross Profit Margin in Relative Terms (% of total input costs) - Vietnam")

```

```{r}

ggplot(hh, aes(x=hhid, color=group)) +
  geom_hline(aes(yintercept=0), color=1) +
  geom_linerange(aes(ymin=0, ymax=margin_ha_ppp), size=.6) +
  geom_point(aes(y=0), shape=20, size=1.4) +
  geom_point(aes(y=margin_ha_ppp, shape=margin_ha_ppp < 0, fill=group), size=1.4) +
  scale_y_continuous(labels=comma) +
  scale_shape_manual(values=24:25) +
  guides(x="none", shape="none") +
  labs(x=NULL, y=NULL, color="", fill="",
    title="Profit Margin (PPP$ / ha) - Vietnam",
    subtitle="Each bar is a respondent's gross profit margin") +
  theme_def(
    legend.position="right",
    panel.grid.major.x=element_blank()
  )

```

Farmers' gross profit margins by gender and across seed clubs in both absolute terms and in relative terms as percentage of total input costs per hectare.

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh, aes(gender, margin_ha_ppp, color=gender, fill=gender), cp=list(1:2)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Absolute Terms - Vietnam",
    subtitle="Stratified by gender (PPP$ / ha)") +
  theme_def(legend.position="none")

ggBoxTest(hh, aes(gender, margin_ha_sh, color=gender, fill=gender), cp=list(1:2)) +
  scale_y_continuous(labels=percent) +
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Relative Terms - Vietnam",
    subtitle="Stratified by gender (% of total costs)") +
  theme_def(legend.position="none")

```

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh, aes(years, margin_ha_ppp, color=years, fill=years), cp=list(1:2)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Absolute Terms - Vietnam",
    subtitle="Stratified by years in seed club (PPP$ / ha)") +
  theme_def(legend.position="none")

ggBoxTest(hh, aes(years, margin_ha_sh, color=years, fill=years), cp=list(1:2)) +
  scale_y_continuous(labels=percent) +
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Relative Terms - Vietnam",
    subtitle="Stratified by years in seed club (% of total costs)") +
  theme_def(legend.position="none")

```

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh, aes(group, margin_ha_ppp, color=group, fill=group)) +
  scale_x_discrete(labels=label_wrap(5)) +
  scale_y_continuous(labels=comma) +  
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Absolute Terms - Vietnam",
    subtitle="Stratified by seed club (PPP$ / ha)") +
  theme_def(legend.position="none")

ggBoxTest(hh, aes(group, margin_ha_sh, color=group, fill=group)) +
  scale_x_discrete(labels=label_wrap(5)) +  
  scale_y_continuous(labels=percent) +  
  labs(x="", y="", fill="",
    title="Gross Profit Margin in Relative Terms - Vietnam",
    subtitle="Stratified by seed club (% of total costs)") +
  theme_def(legend.position="none")

```

```{r}

ggplot(hh[!hhid %in% outlier], aes(member_years, margin_ha_ppp)) +
  geom_smooth(size=.8) +
  geom_point(alpha=.7, shape=20) +
  scale_x_continuous(limits=c(0, 22)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", color="",
    title="Gross Profit Margin in Absolute Terms vs. Years in Seed Club - Vietnam",
    subtitle="Each point is a respondent (years vs. PPP$)") +
  theme_def(legend.position="top")

```

## Correlation

Significant pairwise associations.  

```{r, fig.height=5}

ggpairs(
  hh[, .(`seed club`=group, `age`=age_num, `years in club`=member_years,
    `costs PPP$`=costs_ha_ppp, `seed yield kg/ha`=yield_ha_kg,
    `margin PPP$`=margin_ha_ppp, `margin %`=margin_ha_sh)],
  upper = list(
    continuous="cor", 
    combo=wrap("summarise_by", color=pal[1:5], size=2)),
  lower = list(
    continuous=wrap("smooth", shape=NA), 
    combo=wrap("box_no_facet", fill=pal[1:5], alpha=.8)),
  diag = list(
    continuous=wrap("densityDiag", fill=NA),
    discrete=wrap("barDiag", fill=pal[1:5], alpha=.8)),
  title="Correlogram stratified by seed club - Vietnam"
) + 
  theme_def(
    strip.text=element_text(hjust=.5),
    axis.text.x=element_text(angle=-45),
    panel.grid.major=element_blank()
  )

```

```{r, fig.height=5}

ggpairs(
  hh[, .(gender, `age`=age_num, `years in club`=member_years,
    `costs PPP$`=costs_ha_ppp, `seed yield kg/ha`=yield_ha_kg, 
    `margin PPP$`=margin_ha_ppp, `margin %`=margin_ha_sh)],
  upper = list(
    continuous="cor", 
    combo=wrap("summarise_by", color=pal[1:2], size=2)),
  lower = list(
    continuous=wrap("smooth", shape=NA, color=hh[, pal[gender]]), 
    combo=wrap("box_no_facet", fill=pal[1:2], alpha=.8)),
  diag = list(
    continuous=wrap("densityDiag", fill=NA),
    discrete=wrap("barDiag", fill=pal[1:2], alpha=.8)),
  title="Correlogram stratified by gender - Vietnam"
) +   
  theme_def(
    strip.text=element_text(hjust=.5),
    panel.grid.major=element_blank()
  )

```

```{r, fig.height=5}

ggpairs(
  hh[, .(`years in club`=years, `age`=age_num,
    `costs PPP$`=costs_ha_ppp, `seed yield kg/ha`=yield_ha_kg, 
    `margin PPP$`=margin_ha_ppp, `margin %`=margin_ha_sh)],
  upper = list(
    continuous="cor", 
    combo=wrap("summarise_by", color=pal[1:2], size=2)),
  lower = list(
    continuous=wrap("smooth", shape=NA, color=hh[, pal[gender]]), 
    combo=wrap("box_no_facet", fill=pal[1:2], alpha=.8)),
  diag = list(
    continuous=wrap("densityDiag", fill=NA),
    discrete=wrap("barDiag", fill=pal[1:2], alpha=.8)),
  title="Correlogram stratified by years in seed club - Vietnam"
) +   
  theme_def(
    strip.text=element_text(hjust=.5),
    panel.grid.major=element_blank()
  )

```


```{r save-vnm}

saveRDS(hh, "../tmp/data_vnm.rds")

```

