# Zambia

Notes: 

- 1 Int'l \$ = 5.59 ZMW (Kwacha) using [2020 World Bank PPP conversion rates](https://data.worldbank.org/indicator/PA.NUS.PPP) (1 Int'l \$ = 1 USD)
- Focus crops = **soybean**, **maize**, **cowpea**, **bean**
- All costs are reported per hectare. Inspection, certification and other marketing costs are assumed for the entire farm. Labeling and packaging are per kg.
- Some farmers grow multiple crops


## Survey Recodes

```{r zmb}

xrate <- 5.59

# Load respondent data
hh <- fread("../data/zmb/hh.csv")
group <- fread("../data/zmb/group.csv")

```

There are `r ncol(hh)` variables and `r nrow(hh)` observations in this set. A summary is shown below.

```{r}

print(dfSummary(hh), max.tbl.height=500)

```

Recode variable names (see [codebook](index.html#objectives)).

```{r}

setnames(hh, lbl$label, lbl$code, skip_absent=T)

```

Additional recodes for categorical variables.

```{r}

setorder(hh, adm1_nm, group, gender, crop)

hh[, `:=`(
  hhid = paste("ZMB", gsub(" ", "0", format(1:.N, width=3)), sep=""),
  iso3 = "ZMB",
  crop = factor(crop),
  adm1_nm = factor(adm1_nm),
  # Abbreviate seed club names
  group = factor(group, levels=c(
    "Mweete Seed Growers Association",
    "Tiwine Womens Seed growers Cooperative",
    "Mumbwa Seed Growers Association",
    "Chiyota Seed Growers Association"
  ), labels=c(
    "Mweete",
    "Tiwine",
    "Mumbwa",
    "Chiyota"    
  )),
  gender = factor(gender, levels=c("male", "female"), labels=c("Male", "Female")),
  age = factor(age, levels=c("25", "15-29", "30+"), labels=c("< 30", "< 30", "≥ 30")),
  years = factor(member_years >= 5, levels=c(F, T), labels=c("< 5", "≥ 5"))
)]

```


### Constructed Variables

Farmers report both expected yields `yield_ha_kg` and sales in the last season `sales_ha_kg`, so we can construct both **expected** and **realized** costs in monetary terms `costs_exp_ha_lcu` and `costs_real_ha_lcu`. We use **realized** yields to calculate profitability metrics.

Note that 1 farmer did not report a sales price, so we use the reported median.

```{r}

kbl(caption="Missing sales entry",
  hh[is.na(sales_kg_lcu), 
    .(hhid, code, group, crop, yield_ha_kg, sales_ha_kg, sales_kg_lcu)])

```

```{r}

hh[, 
  tran_ha_lcu := as.numeric(tran_ha_lcu)
][, `:=`(
  tran_ha_lcu = fifelse(is.na(tran_ha_lcu), 0, tran_ha_lcu),
  sales_kg_lcu = fifelse(is.na(sales_kg_lcu), median(sales_kg_lcu, na.rm=T), sales_kg_lcu)
), by=.(group, crop)][, `:=`(
  # Expected costs
  costs_exp_ha_lcu = 
    # Per ha costs
    seed_ha_lcu + fert_ha_lcu + pest_ha_lcu + tran_ha_lcu + labor_ha_lcu + 
    cert_lcu + mark_kg_lcu +
    # Per kg costs
    yield_ha_kg * (labl_kg_lcu + pckg_kg_lcu),  
  # Realized costs
  costs_real_ha_lcu = 
    # Per ha costs
    seed_ha_lcu + fert_ha_lcu + pest_ha_lcu + tran_ha_lcu + labor_ha_lcu + 
    cert_lcu + mark_kg_lcu +
    # Per kg costs
    sales_ha_kg * (labl_kg_lcu + pckg_kg_lcu)
)]

hh[, summary(costs_exp_ha_lcu)]
hh[, summary(costs_real_ha_lcu)]

```

Using **realized** costs and sales, we construct gross margin per ha `margin_ha_lcu`, total sales `sales_ha_sh` and profit margin `margin_ha_sh` per unit of (variable) input costs, and `costs_ha_ppp`, `sales_ha_ppp` and `margin_ha_ppp` in PPP terms to allow for comparisons across groups and countries. 

We also construct a measure of **total factor productivity** `tfp` as **expected** output per unit of (expected) input costs. Strictly speaking it is only "partial factor productivity" here because we don't include the rental cost of land, land preparation costs, irrigation costs, and the costs of animal and mechanical implements.

```{r}

hh[, `:=`(
  sales_exp_ha_lcu = yield_ha_kg * sales_kg_lcu,
  sales_real_ha_lcu = sales_ha_kg * sales_kg_lcu
)][, `:=`(
  margin_ha_lcu = sales_real_ha_lcu - costs_real_ha_lcu
)][, `:=`(
  sales_ha_sh = sales_real_ha_lcu / costs_real_ha_lcu,
  margin_ha_sh = margin_ha_lcu / costs_real_ha_lcu,
  costs_ha_ppp = costs_real_ha_lcu / xrate,
  sales_ha_ppp = sales_real_ha_lcu / xrate,
  margin_ha_ppp = margin_ha_lcu / xrate
)][, `:=`(
  tfp = yield_ha_kg / (costs_exp_ha_lcu / xrate)
)]

```

Below we append some of the information that was recorded at the group level.

```{r}

kbl(group, align="llc")

# Same recodes in the group-level dataset
group[, Group := factor(Group, levels=c(
  "Mweete Seed Growers Association",
  "Tiwine Womens Seed growers Cooperative",
  "Mumbwa Seed Growers Association",
  "Chiyota Seed Growers Association",
  "Kamimpampa Cooperative"
), labels=c(
  "Mweete",
  "Tiwine",
  "Mumbwa",
  "Chiyota",
  "Kamimpampa"
))]

# Merge
hh[group, on=.(group=Group), `:=`(
  group_year = `Established`,
  group_size = `Members`,
  seasons = `Seasons`,
  irrigated = `Irrigation`,
  market_access = `Market access`,
  ttrade = `Transboundary trade`
)]

```

Finally we normalize all farmer cost line items into a "long" table `hh_prod_cost` for charting.

```{r}

# Normalize production cost table per ha
hh_prod_cost <- hh[, .(hhid,
  Seeds = seed_ha_lcu, 
  Fertilizer = fert_ha_lcu, 
  Pesticides = pest_ha_lcu, 
  Labor = labor_ha_lcu, 
  Transport = tran_ha_lcu, 
  Certification = cert_lcu,
  Labeling = sales_ha_kg * labl_kg_lcu,
  Packaging = sales_ha_kg * pckg_kg_lcu,
  Marketing = mark_kg_lcu
)]

hh_prod_cost <- melt(hh_prod_cost, id.vars=1, value.name="lcu", variable.name="type")

```

And we lump all marketing costs into a single category.

```{r}

levels(hh_prod_cost$type) <- levels(hh_prod_cost$type)[c(1,2,3,4,9,9,9,9,9)]

hh_prod_cost <- hh_prod_cost[, .(
  lcu = sum(lcu, na.rm=T)
), by=.(hhid, type)
][, `:=`(
  # Add cost shares and PPP terms
  share = lcu/sum(lcu, na.rm=T),
  ppp = lcu/xrate
), by=.(hhid)
][hh, on=.(hhid), `:=`(
  # Add classes
  group = group,
  gender = gender,
  age = age,
  years = years,
  crop = crop
)]

```


## Descriptive Statistics

### Respondent Characteristics

Breakdown by categorical variables. Note that farmers in HIMMA grow both crops.

```{r, fig.height=4}

ggplot(
  hh[, .N, by=.(group, age, gender, crop, years)],
  aes(axis1=crop, axis2=gender, axis3=age, axis4=years, y=N)) +
  geom_alluvium(aes(fill=group), width=1/4, alpha=.7, color="white") +
  geom_stratum(width=1/4) +
  geom_text(stat="stratum", aes(label=after_stat(stratum)), angle=90, size=2.2) +
  scale_x_discrete(limits=c("Crop", "Gender", "Age", "Years in Seed Club")) +
  labs(y=NULL, fill="Seed Club",
    title = "Categories of Survey Respondents - Zambia",
    subtitle = "Stratified by seed club") +
  theme_def(axis.text=element_text(face="bold"))

```

Showing contingency table between each pair of categorical variables (seed club `group`, `gender`, age `age`, and years in seed club `years`).

```{r}

ttt_ftable(hh, vars=c("group", "gender", "years"))

```


### Seed Production Costs

General breakdown and distribution of input costs across seed clubs, gender, years in seed club, and input type.

```{r}

ttt(costs_ha_ppp ~ group | gender+years, data=hh, render=fmt,
  caption="Total Input Costs in Absolute Terms (PPP$ / ha) - Zambia")

```

Boxplots with mean comparison p-value and significance levels. When more than two levels, each level is **compared to the group mean**.

(ns : p > 0.05, * : p ≤ 0.05, ** : p ≤ 0.01, *** = p ≤ 0.001, **** = p ≤ 0.0001)

Note that `r hh[costs_ha_ppp > 1000, .N]` farmers have total input costs above PPP$ 800/ha.

```{r}

outlier <- hh[costs_ha_ppp > 1000, hhid]

kbl(caption="Outliers",
  hh[hhid %in% outlier, .(hhid, code, group, crop, costs_ha_ppp)],
  format.args=list(big.mark=",", digits=0))

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, costs_ha_ppp, color=gender, fill=gender), 
  grp.c=aes(group=crop), grp.s=aes(group=gender)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="", color="",
    title="Total Input Costs (PPP$ / ha) - Zambia",
    subtitle="Stratified by crop and gender") +
  theme_def(legend.position="top")

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, costs_ha_ppp, color=group, fill=group),
  grp.c=aes(group=crop), grp.s=aes(group=group)) +
  scale_y_continuous(labels=comma) + 
  labs(x="", y="", fill="", color="",
    title="Total Input Costs (PPP$ / ha) - Zambia",
    subtitle="Stratified by crop") +
  theme_def(legend.position="top")

```

Breakdown across categories of farm input.

```{r}

ttt(ppp ~ type | gender+crop, data=hh_prod_cost, render=fmt,
  caption="Input Costs in Absolute Terms by Gender (PPP$ / ha) - Zambia")

```

```{r}

tbl <- hh_prod_cost[, .(
  ppp = mean(ppp, na.rm=T)
), keyby=.(gender, crop, type)]

ggplot(tbl, aes(gender, ppp, fill=type)) +
  geom_bar(stat="identity", position="fill", alpha=.7, width=.6, color="white") +
  scale_y_continuous(labels=percent) +
  facet_wrap(~crop, nrow=1) +
  labs(y="", x="", fill="",
    title="Breakdown of Input Costs by Category - Zambia",
    subtitle="Stratified by crop and gender") +
  theme_def(legend.position="right")

```

```{r}

ttt(ppp ~ type | years+crop, data=hh_prod_cost, render=fmt,
  caption="Input Costs in Absolute Terms by Years in Seed Group (PPP$ / ha) - Zambia")

```

```{r}

tbl <- hh_prod_cost[, .(
  ppp = mean(ppp, na.rm=T)
), keyby=.(years, crop, type)]

ggplot(tbl, aes(years, ppp, fill=type)) +
  geom_bar(stat="identity", position="fill", alpha=.7, width=.6, color="white") +
  scale_y_continuous(labels=percent) +
  facet_wrap(~crop, nrow=1) +
  labs(y="", x="",
    title="Breakdown of Input Costs by Category - Zambia",
    subtitle="Stratified by crop and years in seed club") +
  theme_def(legend.position="right")

```

```{r}

ttt(ppp ~ type | group+crop, data=hh_prod_cost, render=fmt,
  caption="Input Costs in Absolute Terms by Seed Group (PPP$ / ha) - Zambia")

```

```{r}

tbl <- hh_prod_cost[, .(
  ppp = mean(ppp, na.rm=T)
), keyby=.(group, crop, type)]

ggplot(tbl, aes(group, ppp, fill=type)) +
  geom_bar(stat="identity", position="fill", alpha=.7, width=.6, color="white") +
  scale_y_continuous(labels=percent) +
  facet_wrap(~crop, scales="free_x", nrow=1) +
  labs(y="", x="",
    title="Breakdown of Input Costs by Category - Zambia",
    subtitle="Stratified by crop and seed club") +
  theme_def(legend.position="top")

```

Are there significant differences across groups? We first compare input cost shares across gender, then across seed clubs.

```{r, fig.height=4}

ggBoxTest(hh_prod_cost[!type %in% c("Seeds")], 
  aes(type, share, color=gender, fill=gender),
  grp.c=aes(group=type), grp.s=aes(group=gender), jitter=F) +
  scale_y_continuous(labels=percent) +
  #facet_wrap(~crop) +  
  labs(x="", y="", fill="", color="",
    title="Input Costs by Category (Percent of Total Costs by Ha) - Zambia",
    subtitle="Stratified by gender") +
  theme_def(legend.position="right")

```

Differences across years in seed club.

```{r, fig.height=4}

ggBoxTest(hh_prod_cost[!type %in% c("Seeds")], 
  aes(type, share, color=years, fill=years),
  grp.c=aes(group=type), grp.s=aes(group=years), jitter=F) +
  scale_y_continuous(labels=percent) +
  #facet_wrap(~crop) +  
  labs(x="", y="", fill="", color="",
    title="Input Costs by Category (Percent of Total Costs by Ha) - Zambia",
    subtitle="Stratified by years in seed club") +
  theme_def(legend.position="right")

```

Differences across seed clubs.

```{r}

ggBoxTest(hh_prod_cost[!type %in% c("Seeds")], 
  aes(type, share, color=group, fill=group),
  grp.c=aes(group=type), grp.s=aes(group=group), jitter=F) +
  scale_y_continuous(labels=percent) +
  #facet_wrap(~crop) +  
  labs(x="", y="", fill="", color="",
    title="Input Costs by Category (PPP$ by Hectare) - Zambia",
    subtitle="Stratified by seed club") +
  theme_def(legend.position="right")

```

Differences across crops.

```{r}

ggBoxTest(hh_prod_cost[!type %in% c("Seeds")], 
  aes(type, share, color=crop, fill=crop),
  grp.c=aes(group=type), grp.s=aes(group=crop), jitter=F) +
  scale_y_continuous(labels=percent) +
  labs(x="", y="", fill="", color="",
    title="Input Costs by Category (PPP$ by Hectare) - Zambia",
    subtitle="Stratified by crop") +
  theme_def(legend.position="top")

```


### Efficiency

Differences in productivity measures (expected seed yields and actual sales) across groups.

```{r}

ttt(yield_ha_kg ~ group | gender+crop, data=hh, render=fmt,
  caption="Expected Seed Yield (kg / ha) - Zambia")
ttt(sales_ha_kg ~ group | gender+crop, data=hh, render=fmt,
  caption="Realized Seed Sales (kg / ha) - Zambia")

ttt(yield_ha_kg ~ group | years+crop, data=hh, render=fmt,
  caption="Realized Seed Sales (kg / ha) - Zambia")
ttt(sales_ha_kg ~ group | years+crop, data=hh, render=fmt,
  caption="Realized Seed Sales (kg / ha) - Zambia")

```

Differences in efficiency measures across gender with mean comparison (Wilcoxon) p-value. Note the we take out outlying values.

```{r}

outlier <- c(
  hh[yield_ha_kg > median(yield_ha_kg) + 3*sd(yield_ha_kg), hhid],
  hh[sales_ha_ppp > median(sales_ha_ppp) + 3*sd(yield_ha_kg), hhid]
)

kbl(caption="Respondents with yields or sales > median + 3*sd",
  hh[hhid %in% outlier, .(hhid, code, group, crop, yield_ha_kg, sales_ha_ppp)],
  format.args=list(big.mark=","))

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, yield_ha_kg, color=gender, fill=gender),
  grp.c=aes(group=crop), grp.s=aes(group=gender)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="", color="",
    title="Expected Seed Yield (kg / ha) - Zambia",
    subtitle="Stratified by crop and gender") +
  theme_def(legend.position="top")

ggBoxTest(hh[!hhid %in% outlier],
  aes(crop, sales_ha_ppp, color=gender, fill=gender),
  grp.c=aes(group=crop), grp.s=aes(group=gender)) +  
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="", color="",
    title="Total Seed Sales (PPP$ / ha) - Zambia",
    subtitle="Stratified by gender") +
  theme_def(legend.position="top")

```

Differences in efficiency measures by years in seed club with mean comparison (Wilcoxon) p-value.

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, yield_ha_kg, color=years, fill=years),
  grp.c=aes(group=crop), grp.s=aes(group=years)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="", color="",
    title="Expected Seed Yield (kg / ha) - Zambia",
    subtitle="Stratified crop and by years in seed club") +
  theme_def(legend.position="top")

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, sales_ha_ppp, color=years, fill=years),
  grp.c=aes(group=crop), grp.s=aes(group=years)) + 
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="", color="",
    title="Total Seed Sales (PPP$ / ha) - Zambia",
    subtitle="Stratified crop and by years in seed club") +
  theme_def(legend.position="top")

```

Differences in efficiency measures across seed clubs with global ANOVA p-value.

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, yield_ha_kg, color=group, fill=group),
  grp.c=aes(group=crop), grp.s=aes(group=group)) + 
  scale_x_discrete(labels=label_wrap(5)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="", color="",
    title="Expected Seed Yield (Kg / ha) - Zambia",
    subtitle="Stratified by crop and seed club") +
  theme_def(legend.position="top")

ggBoxTest(hh[!hhid %in% outlier],
  aes(crop, sales_ha_ppp, color=group, fill=group),
  grp.c=aes(group=crop), grp.s=aes(group=group)) + 
  scale_x_discrete(labels=label_wrap(5)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="", color="",
    title="Total Seed Sales (PPP$ / ha) - Zambia",
    subtitle="Stratified crop by seed club") +
  theme_def(legend.position="top")

```

Looking at **production frontiers** (units of output vs. units of input). We expect S-shape curves with farmers at different levels of technical efficiency along the curve. 

Note that in the approximated curves below we remove outliers with total input costs over PPP$ 1,700 per ha.

```{r, fig.width=6}

outlier <- hh[costs_ha_ppp > median(costs_ha_ppp) + 3*sd(costs_ha_ppp), hhid]

kbl(
  caption="Farmers with total input costs > median + 3*sd",
  hh[hhid %in% outlier, .(hhid, group, crop, yield_ha_kg, costs_ha_ppp)],
  format.args=list(big.mark=",", digits=0))

ggplot(hh[!hhid %in% outlier], aes(costs_ha_ppp, yield_ha_kg)) +
  geom_smooth(size=.8) +
  geom_point(alpha=.7, shape=20, color=1) +
  scale_x_continuous(labels=comma) +
  scale_y_continuous(labels=comma) +
  facet_wrap(~crop, scales="free", nrow=1) +
  labs(x="", y="",
    title="Production Frontier (Output vs. Input) - Zambia",
    subtitle="Each point is a respondent. Shade shows 90% CI (kg vs. PPP$ / ha)") +
  theme_def(legend.position="none")

```


### Profitability

Farmers' gross profit margins by crop, gender, and years in seed club.

```{r}

ttt(margin_ha_ppp ~ group+crop | gender+years, data=hh, render=fmt,
  caption="Mean Gross Profit Margin in Absolute Terms (PPP$ / ha) - Zambia")

ttt(margin_ha_sh ~ group+crop | gender+years, data=hh, render=fmt_pct,
  caption="Mean Gross Profit Margin in Relative Terms (% of variable input costs) - Zambia")

```

Note that `r hh[margin_ha_ppp < 0, .N]` respondents show negative margins.

```{r}

kbl(caption="Respondents with negative gross margins.",
  hh[margin_ha_ppp < 0, 
    .(hhid, code, group, crop, costs_ha_ppp, yield_ha_kg, sales_ha_kg, margin_ha_ppp)],
  format.args=list(big.mark=",", digits=1))

outlier <- c(
  hh[margin_ha_ppp > median(margin_ha_ppp) + 3*sd(margin_ha_ppp), hhid],
  hh[margin_ha_sh > median(margin_ha_sh) + 3*sd(margin_ha_sh), hhid]
)

kbl(caption="Respondents with gross margins > median + 3*sd",
  hh[hhid %in% outlier, 
    .(hhid, code, group, crop, costs_ha_ppp, yield_ha_kg, sales_ha_kg, 
      margin_ha_ppp, margin_ha_sh)],
  format.args=list(big.mark=",", digits=1))

```

```{r}

ggplot(hh, aes(x=hhid, color=group)) +
  geom_hline(aes(yintercept=0), color=1) +
  geom_linerange(aes(ymin=0, ymax=margin_ha_ppp), size=.6) +
  geom_point(aes(y=0), shape=20, size=1.4) +
  geom_point(aes(y=margin_ha_ppp, shape=margin_ha_ppp < 0, fill=group), size=1.4) +
  scale_y_continuous(labels=comma) +
  scale_shape_manual(values=24:25) +
  guides(x="none", shape="none") +
  labs(x=NULL, y=NULL, color="", fill="",
    title="Profit Margin (PPP$ / ha) - Zambia",
    subtitle="Each bar is a respondent's gross profit margin") +
  theme_def(
    legend.position="right",
    panel.grid.major.x=element_blank()
  )

```

Farmers' gross profit margins by gender and across groups in both absolute and relative terms (as percentage of total costs per hectare).

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, margin_ha_ppp, color=gender, fill=gender),
  grp.c=aes(group=crop), grp.s=aes(group=gender)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="", color="",
    title="Gross Profit Margin in Absolute Terms - Zambia",
    subtitle="Stratified by crop and gender (PPP$ / ha)") +
  theme_def(legend.position="top")

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, margin_ha_sh, color=gender, fill=gender),
  grp.c=aes(group=crop), grp.s=aes(group=gender)) +
  scale_y_continuous(labels=percent) +
  labs(x="", y="", fill="", color="",
    title="Gross Profit Margin in Relative Terms - Zambia",
    subtitle="Stratified by crop and gender (% of total costs)") +
  theme_def(legend.position="top")

```

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, margin_ha_ppp, color=years, fill=years),
  grp.c=aes(group=crop), grp.s=aes(group=years)) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", fill="", color="",
    title="Gross Profit Margin in Absolute Terms - Zambia",
    subtitle="Stratified by crop and years in seed club (PPP$ / ha)") +
  theme_def(legend.position="top")

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, margin_ha_sh, color=years, fill=years),
  grp.c=aes(group=crop), grp.s=aes(group=years)) +
  scale_y_continuous(labels=percent) +
  labs(x="", y="", fill="", color="",
    title="Gross Profit Margin in Relative Terms - Zambia",
    subtitle="Stratified by crop and years in seed club (% of total costs)") +
  theme_def(legend.position="top")

```

```{r, out.width="50%", fig.width=2.5, fig.show="hold", fig.asp=1}

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, margin_ha_ppp, color=group, fill=group),
  grp.c=aes(group=crop), grp.s=aes(group=group)) +
  scale_x_discrete(labels=label_wrap(5)) +
  scale_y_continuous(labels=comma) + 
  labs(x="", y="", color="", fill="",
    title="Gross Profit Margin in Absolute Terms - Zambia",
    subtitle="Stratified by crop and seed club (PPP$ / ha)") +
  theme_def(legend.position="top")

ggBoxTest(hh[!hhid %in% outlier], 
  aes(crop, margin_ha_sh, color=group, fill=group),
  grp.c=aes(group=crop), grp.s=aes(group=group)) +
  scale_x_discrete(labels=label_wrap(5)) +  
  scale_y_continuous(labels=percent) +
  labs(x="", y="", color="", fill="",
    title="Gross Profit Margin in Relative Terms - Zambia",
    subtitle="Stratified by crop and seed club (% of total costs)") +
  theme_def(legend.position="top")

```

```{r}

ggplot(hh[!hhid %in% outlier], aes(member_years, margin_ha_ppp)) +
  geom_smooth(size=.8) +
  geom_point(alpha=.7, shape=20) +
  scale_y_continuous(labels=comma) +
  labs(x="", y="", color="",
    title="Gross Profit Margin in Absolute Terms vs. Years in Seed Club - Zambia",
    subtitle="Each point is a respondent (years vs. PPP$)") +
  theme_def(legend.position="top")

```


## Correlation

Significant pairwise associations. 

```{r, fig.height=5}

ggpairs(
  hh[, .(`seed club`=group, `years in club`=member_years,
    `costs PPP$`=costs_ha_ppp, `seed yield kg/ha`=yield_ha_kg,
    `margin PPP$`=margin_ha_ppp, `margin %`=margin_ha_sh)],
  upper = list(
    continuous="cor", 
    combo=wrap("summarise_by", color=pal[1:4], size=2)),
  lower = list(
    continuous=wrap("smooth", shape=NA), 
    combo=wrap("box_no_facet", fill=pal[1:4], alpha=.8)),
  diag = list(
    continuous=wrap("densityDiag", fill=NA),
    discrete=wrap("barDiag", fill=pal[1:4], alpha=.8)),
  title="Correlogram stratified by seed club - Zambia"
) + 
  theme_def(
    strip.text=element_text(hjust=.5),
    axis.text.x=element_text(angle=-45),
    panel.grid.major=element_blank()
  )

```

```{r, fig.height=5}

ggpairs(
  hh[, .(gender, `years in club`=member_years,
    `costs PPP$`=costs_ha_ppp, `seed yield kg/ha`=yield_ha_kg, 
    `margin PPP$`=margin_ha_ppp, `margin %`=margin_ha_sh)],
  upper = list(
    continuous="cor", 
    combo=wrap("summarise_by", color=pal[1:2], size=2)),
  lower = list(
    continuous=wrap("smooth", shape=NA, color=hh[, pal[gender]]), 
    combo=wrap("box_no_facet", fill=pal[1:2], alpha=.8)),
  diag = list(
    continuous=wrap("densityDiag", fill=NA),
    discrete=wrap("barDiag", fill=pal[1:2], alpha=.8)),
  title="Correlogram stratified by gender - Zambia"
) +   
  theme_def(
    strip.text=element_text(hjust=.5),
    panel.grid.major=element_blank()
  )

```

```{r, fig.height=5}

ggpairs(
  hh[, .(`years in club`=years,
    `costs PPP$`=costs_ha_ppp, `seed yield kg/ha`=yield_ha_kg, 
    `margin PPP$`=margin_ha_ppp, `margin %`=margin_ha_sh)],
  upper = list(
    continuous="cor", 
    combo=wrap("summarise_by", color=pal[1:2], size=2)),
  lower = list(
    continuous=wrap("smooth", shape=NA, color=hh[, pal[gender]]), 
    combo=wrap("box_no_facet", fill=pal[1:2], alpha=.8)),
  diag = list(
    continuous=wrap("densityDiag", fill=NA),
    discrete=wrap("barDiag", fill=pal[1:2], alpha=.8)),
  title="Correlogram stratified by years in seed club - Zambia"
) +   
  theme_def(
    strip.text=element_text(hjust=.5),
    panel.grid.major=element_blank()
  )

```

```{r save-zmb}

saveRDS(hh, "../tmp/data_zmb.rds")

```

```{r}

# Combine all country datasets
gtm <- readRDS("../tmp/data_gtm.rds")
nre <- readRDS("../tmp/data_nre.rds")
vnm <- readRDS("../tmp/data_vnm.rds")
zmb <- readRDS("../tmp/data_zmb.rds")
vars <- lbl$code
hh <- rbindlist(list(
  gtm[, .SD, .SDcols=names(gtm) %in% vars], 
  nre[, .SD, .SDcols=names(nre) %in% vars], 
  vnm[, .SD, .SDcols=names(vnm) %in% vars], 
  zmb[, .SD, .SDcols=names(zmb) %in% vars]
), fill=T)
setcolorder(hh, lbl[code %in% names(hh), unique(code)])
fwrite(hh, "../data/hh.csv")

```
